%sample template for submission for research paper write-ups

%author : Muhammad Falak R Wani (mfrw)

%Course : CSE545 (FCS)


\documentclass[11pt]{article}
\usepackage[pdftex]{graphicx, color}
\usepackage{listings}

\usepackage{tikz}
\usetikzlibrary{automata,positioning}

\headheight 8pt \headsep 20pt \footskip 30pt
\textheight 9in \textwidth 6.5in
\oddsidemargin 0in \evensidemargin 0in
\topmargin -.35in

\lstset{basicstyle=\small\ttfamily,breaklines=true}

\begin{document}
\begin{center}
%% Change this:
\LARGE CSE 345/545: Foundations to Computer Security \\
\Large Homework Assignment I (\textbf{100} Points) \\
\Large Due: \texttt{2100hrs 31 August 2017} \\
Plagiarism policies will be strictly enforced. \\
\end{center}

\\
\\
\noindent {\Large Part I} [\texttt{20 points}] \\\\
Classify the below mentioned passwords as very strong, strong, neutral, weak, very weak and also, justify your reasoning. Please keep the response within 20 words for each.
\begin{enumerate}
\item Alice
\item Qwerty1234
\item Rat\$you
\item 0xd34db33F
\item Mumb4i
\item Mfiical4W [\textbf{M}y\textbf{f}amily\textbf{i}s\textbf{i}n\textbf{Cal}ifornia\textbf{for}\textbf{W}ork]
\item \begin{verbatim}Tif#hom&851@ \end{verbatim} 
\item \begin{verbatim} #$\%@$^$^@$@#  \end{verbatim} 
\item ecila!0987 [reverse of Alice] 
\item 45649243 \\\\

\end{enumerate}

\noindent {\Large Part II} [\texttt{30 points}] \\\\
Design an authentication, authorization and identification scheme for visitors, students, faculty, and employees of IIIT-Delhi.

\begin{itemize}
    \item Describe the complete design of the system and how each of the components will be incorporated?
    \item Discuss various (at least 3) ways in which attacker might try to spoof the system. 
    \item Give countermeasures that you have taken to avoid the spoofing and other attacks.
\end{itemize}

\noindent Please keep your complete response within 800--1000 words.\\\\

\newpage
\noindent {\Large Part III} [\texttt{30 points}] \\\\
Reverse the following Ciphertext:

\begin{verbatim}
    slnpzshabylzohssthrluvshdylzwljapunhulzahispzotlu
    avmylspnpvuvywyvopipapunaolmylllelyjpzlaolylvmvyh
    iypknpunaolmyllkvtvmzwlljovyvmaolwylzzvyaolypnoav
    maolwlvwslwlhjlhisfavhzzltislhukavwlapapvuaolnvcl
    yutluamvyhylkylzzvmnyplchujlz
\end{verbatim}

\begin{itemize}
\item Provide the plain text
\item Provide working code for reversing this. \texttt{(Any programming language)}
\item Describe the methodology, in detail, used for reversing the cipher text.

\end{itemize}

\noindent Please keep your complete response concise and to the point.\\\\

\noindent {\Large Part IV} [\texttt{20 points}] \\\\
Pick a secure system (email authentication, etc.) that you are using in everyday life and suggest ways to make it usable. Address the topics that we discussed in class. Keep the answer less than 500 words. In your proposed system, please discuss: 

\begin{itemize}
\item What usability issues you feel need to be addressed? 
\item Include some suggestions to improve the system. 

\end{itemize}

\noindent Remember there is a trade-off, the scheme should provide reasonable security at least..
\\\\\\

\noindent{\textbf{Submission guidelines (points will be deducted if not followed): Please post it onto Backpack by the deadline. Do not send it by email! No email submissions will be entertained. }}
\end{document}

